MSTK: Mesh Toolkit, v 1.2 - DRAFT

### 2004-01-27 docs/MSTK.tex
Updated version 1.2 manual with an example

% TeX calculates margins from a point 1 inch from the top and 1 inch
% from the left of the page. So the total left margin for instance is
% the 'oddsidemargin' + 1 inch.
%
%\setlength{\textwidth}{4.5in}
%\setlength{\textheight}{7.0in}
%\setlength{\evensidemargin}{0.0in}
%\setlength{\oddsidemargin}{0.0in}
%\setlength{\topmargin}{0.5in}

@@

\title{MSTK: Mesh Toolkit, v 1.1 - DRAFT}

@@

\begin{figure}[!h]
%  \begin{center}
    \begin{minipage}{2.525in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repF1} \\
        Representation F1
      \end{center}
    \end{minipage}\hfill%
    \begin{minipage}{2.525in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repF4} \\
        Representation F4
      \end{center}
    \end{minipage}
    \vspace{5em}

    \begin{minipage}{1.75in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repR1} \\
        Representation R1
      \end{center}
    \end{minipage}
    \begin{minipage}{1.75in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repR2} \\
        Representation R2
      \end{center}
    \end{minipage}
    \begin{minipage}{1.75in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repR4} \\
        Representation R4
      \end{center}
    \end{minipage}
%  \end{center}
\end{figure}

@@

>>>>

% TeX calculates margins from a point 1 inch from the top and 1 inch
% from the left of the page. So the total left margin for instance is
% the 'oddsidemargin' + 1 inch.
%
\setlength{\textwidth}{6.5in}
%\setlength{\textheight}{7.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\oddsidemargin}{0.0in}
%\setlength{\topmargin}{0.5in}

@@

\title{MSTK: Mesh Toolkit, v 1.2 - DRAFT}

@@

\begin{figure}[!ht]
  \begin{center}
    \begin{minipage}{2.525in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repF1} \\
        Representation F1
      \end{center}
    \end{minipage}
    \begin{minipage}{2.525in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repF4} \\
        Representation F4
      \end{center}
    \end{minipage}
    \vspace{5em}

    \begin{minipage}{1.75in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repR1} \\
        Representation R1
      \end{center}
    \end{minipage}
    \begin{minipage}{1.75in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repR2} \\
        Representation R2
      \end{center}
    \end{minipage}
    \begin{minipage}{1.75in}
      \begin{center}
        \includegraphics[scale=0.9]{figures/repR4} \\
        Representation R4
      \end{center}
    \end{minipage}
  \end{center}
\end{figure}

@@

\section{Example program}

NOTE: This program is included in the distribution.

\begin{verbatim}
#include <stdio.h>
#include <stdlib.h>
#include "MSTK.h"
#include "test.h"

int main(int argc, char *argv[]) {
 int i, idx, idx2, ok, edir, nv, ne;
 double xyz[3];
 char meshname[256];
 Mesh_ptr mesh;
 MVertex_ptr v;
 MEdge_ptr e;
 MFace_ptr f;
 GEntity_ptr gent;
 List_ptr fedges;

 /* Initialize MSTK - Always do this even if it does
    not seem to matter in this version of MSTK */

 MSTK_Init();

 /* Load the mesh */

 strcpy(meshname,argv[1]);
 strcat(meshname,".mstk");

 mesh = MESH_New(UNKNOWN_REP);
 ok = MESH_InitFromFile(mesh,meshname);
 if (!ok) {
   fprintf(stderr,"Cannot file input file %s\n\n\n",meshname);
   exit(-1);
 }

 /* Print some info about the mesh */

 nv = MESH_Num_Vertices(mesh);
 for (i = 0; i < nv; i++) {
  v = MESH_Vertex(mesh,i);

  /* Basic info */
  printf("\n");
  printf("Vertex: 0x%-x   ID: %-d   ",v,MV_ID(v));

  /* Classification w.r.t. geometric model */

  if (MV_GEntDim(v) == -1)
    fprintf(stderr,"Unknown Classification\n");
  else {
   printf("GEntID: %-d   GEntDim: %-d\n",MV_GEntID(v),MV_GEntDim(v));
   if ((gent = MV_GEntity(v)))
     printf("Model entity pointer: 0x%-x\n",gent);   
  }

  /* Coordinates */
  MV_Coords(v,xyz);
  printf("Coords: %16.8lf %16.8lf %16.8lf\n",xyz[0],xyz[1],xyz[2]);
 }

 idx = 0;
 while (f = MESH_Next_Face(mesh,&idx)) {

  /* Basic info */
  printf("\n");
  printf("Face: 0x%-x   ID: %-d   ",f,MF_ID(f));

  /* Classification w.r.t. geometric model */

  if (MF_GEntDim(f) == -1)
   fprintf(stderr,"Unknown Classification\n");
  else {
   printf("GEntID: %-d   GEntDim: %-d\n",MF_GEntID(f),MF_GEntDim(f));
   if ((gent = MF_GEntity(f)))
    printf("Model entity pointer: 0x%-x\n",gent);
  }
  printf("\n");

  /* Edges of face */
  fedges = MF_Edges(f,1,0);
  ne = List_Num_Entries(fedges);
  printf("Edges: %-d\n",ne);
  printf("Object       ID     GEntID  GEntDim   Vertex IDs\n");
  idx2 = 0; i = 0;
  while (e = List_Next_Entry(fedges,&idx2)) {
   edir = MF_EdgeDir_i(f,i);
   if (edir) 
    printf("0x%-8x    %-8d %-8d     %-1d       %-d  %-d\n",
           e,ME_ID(e),ME_GEntID(e),ME_GEntDim(e),
           MV_ID(ME_Vertex(e,0)),MV_ID(ME_Vertex(e,1)));
   else 
    printf("0x%-8x    %-8d %-8d     %-1d       %-d  %-d\n",
           e,-ME_ID(e),ME_GEntID(e),ME_GEntDim(e),
           MV_ID(ME_Vertex(e,0)),MV_ID(ME_Vertex(e,1)));
   i++;
  }
  printf("\n");
  List_Delete(fedges);
 }

 /* Write out a copy of the mesh */

 strcpy(meshname,argv[1]);
 strcat(meshname,"-copy.mstk");
 MESH_WriteToFile(mesh,meshname);

 /* No need to delete a mesh if program ends right afterwards */

 MESH_Delete(mesh);
 return 1;
}
\end{verbatim}
